Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)

### 2024-12-03 paper/paper.qmd
Upload datasheet name

---
title: "Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)"
subtitle: "Analysis using data from Toronto’s Committee of Adjustment applications using Bayesian Logistic Regression"
author: Victoria Zheng
thanks: "Code and data are available at: [https://github.com/Anjojoo/Committee-of-Adjustment-Applications](https://github.com/Anjojoo/Committee-of-Adjustment-Applications)."
date: today
date-format: long
abstract: "This paper analyzes urban planning application approvals submitted to Toronto's Committee of Adjustment from 2016 to 2024, focusing on key predictors such as application type, submission year, and planning district using Bayesian logistic regression. The analysis shows that consents are more likely to be approved than minor variances, with approval rates generally increasing over time, particularly from 2017 onward, though fluctuations are observed in certain years. Geographic disparities were identified, with North York showing the highest likelihood of approval, while Scarborough faced stricter reviews. These findings enhance understanding of urban planning decision-making processes, offering insights into temporal trends, geographic variability, and areas for equitable policy adjustments."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

- Your answers will be treated with complete confidentiality.
- Participation in this survey is voluntary.
- You are encouraged to provide honest and thoughtful responses.
- The survey is estimated to take about 5 minutes to complete.
- If you have any questions or concerns, feel free to reach out to me at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca) (Victoria Zheng).

@@

If you have any questions or would like to learn more about this study, please don’t hesitate to contact our research team at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca) (Victoria Zheng).

>>>>

---
title: "Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)"
subtitle: "Analysis using data from Toronto’s Committee of Adjustment applications using Bayesian Logistic Regression"
author: Angel Xu
thanks: "Code and data are available at: [https://github.com/Anjojoo/Committee-of-Adjustment-Applications](https://github.com/Anjojoo/Committee-of-Adjustment-Applications)."
date: today
date-format: long
abstract: "This paper analyzes urban planning application approvals submitted to Toronto's Committee of Adjustment from 2016 to 2024, focusing on key predictors such as application type, submission year, and planning district using Bayesian logistic regression. The analysis shows that consents are more likely to be approved than minor variances, with approval rates generally increasing over time, particularly from 2017 onward, though fluctuations are observed in certain years. Geographic disparities were identified, with North York showing the highest likelihood of approval, while Scarborough faced stricter reviews. These findings enhance understanding of urban planning decision-making processes, offering insights into temporal trends, geographic variability, and areas for equitable policy adjustments."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

- Your answers will be treated with complete confidentiality.
- Participation in this survey is voluntary.
- You are encouraged to provide honest and thoughtful responses.
- The survey is estimated to take about 5 minutes to complete.
- If you have any questions or concerns, feel free to reach out to me at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca) (Angel Xu).

@@

If you have any questions or would like to learn more about this study, please don’t hesitate to contact our research team at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca) (Angel Xu).
